---
title: "montecarlo"
author: "Planning & Regional Development"
date: "5/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#install.packages("MonteCarlo") 
library(MonteCarlo)
```

So, we're buying stock in Black Flag (roach motels). Average returns are 7% (SD is 9%). 

```{r}
set.seed(239) 
returns = rnorm(1:100, mean = 9, sd = 12) # rnorm: normal distribution 
```

```{r}
hist(returns)
```


We want to ignore it for five years, then check in to see where it's landed. 
```{r}
sample(returns,size = 5)
```
That's five years of returns. But try again ... 
```{r}
sample(returns,size = 4)
```
... and there are five different returns. 

A quick Monte Carlo tells us what to expect. You sample from the vector of potential returns, then take the mean for each year. 

```{r}
X = matrix(ncol = 5,nrow = 1000)
for(year in 1:5) {
# for each year, sample the return 1000 times
 for(i in 1:1000){
  X[i,year] = sample(returns,1)
 }
}

head(X)
```

Grab the column means for an expectation for each year: 
```{r}
apply(X,2,mean)
```



# Outbreaks 
OK, so there may be up to three subsequent outbreaks and three associated lockdowns. 

```{r}
set.seed(239) 
returns = rnorm(1:100, mean = 9, sd = 12) # rnorm: normal distribution 
```

```{r}
hist(returns)
```


We want to ignore it for five years, then check in to see where it's landed. 
```{r}
sample(returns,size = 5)
```
That's five years of returns. But try again ... 
```{r}
sample(returns,size = 4)
```
... and there are five different returns. 

A quick Monte Carlo tells us what to expect. You sample from the vector of potential returns, then take the mean for each year. 

```{r}
X = matrix(ncol = 5,nrow = 1000)
for(year in 1:5) {
# for each year, sample the return 1000 times
 for(i in 1:1000){
  X[i,year] = sample(returns,1)
 }
}

head(X)
```

Grab the column means for an expectation for each year: 
```{r}
apply(X,2,mean)
```

